Wigglyhedra

### 2024-02-28 draft/wigglyhedra.tex
Updated arc construction in inverse bijection.
A couple of minor questions/corrections.

% marginal comments
\usepackage{todonotes}
\newcommand{\vincent}[1]{\todo[color=blue!30]{\rm #1 \\ \hfill --- V.}}

@@

We consider sets of compatible wiggly arcs.
The following definitions are illustrated~in~\cref{fig:pseudodissections}.

@@

\begin{proof}
Consider any internal wiggly arc~$\alpha$ of a wiggly pseudotriangulation~$T$.
Then~$Q \eqdef T \ssm \{\alpha\}$ contains~$n-2$ wiggly pseudotriangles and $1$ pseudoquadrangle~$q$.
By \cref{prop:diagonalsPseudoquadrangle}, $q$ admits precisely two wiggly diagonals, $\alpha$ and an other one~$\alpha'$.
As $\alpha'$ is inside~$q$ and compatible with~$c$, it is also compatible with~$Q$.
We obtain that~$T' \eqdef Q \cup \{\alpha'\}$ is the only wiggly pseudotriangulation other than~$T$ containing~$Q$.
\end{proof}

@@

\begin{definition}
\label{def:bijection2}
For a wiggly permutation~$\sigma$ of~$[2n]$, we define~$\Psi(\sigma) \eqdef \set{\alpha(\sigma, k)}{k \in [2n-1]}$, where for~$k \in [2n-1]$, we have~$\alpha(\sigma, k) \eqdef \big( i, j, {]i,j[} \cap \sigma([k]), {]i,j[} \ssm \sigma([k]) \big)$ with
\[
i \eqdef \max \{0\} \cup \set{i \in [n]}{2i-1 \in \sigma([k]) \not\ni 2i} 
\;\text{and}\;
j \eqdef \min \{n+1\} \cup \set{j \in [n]}{2j \in \sigma([k]) \not\ni 2j-1} \!.
\]
\end{definition}

>>>>

% marginal comments
\usepackage{todonotes}
\newcommand{\vincent}[1]{\todo[color=blue!30]{\rm #1 \\ \hfill --- V.}}
\newcommand{\asilata}[2][]{\todo[size=\scriptsize, color=orange!30,#1]{\rm #2 \\ \hfill --- A.}}

@@

We consider sets of compatible wiggly arcs.
The following definitions are illustrated~in~\cref{fig:pseudodissections}.\asilata{It looks like the degree of the green cell is 6 in the figure, not 8.}

@@

\begin{proof}
Consider any internal wiggly arc~$\alpha$ of a wiggly pseudotriangulation~$T$.
Then~$Q \eqdef T \ssm \{\alpha\}$ contains~$n-2$ wiggly pseudotriangles and $1$ pseudoquadrangle~$q$.
By \cref{prop:diagonalsPseudoquadrangle}, $q$ admits precisely two wiggly diagonals, $\alpha$ and another one~$\alpha'$.
As $\alpha'$ is inside~$q$ and compatible with~$c$, it is also compatible with~$Q$.
We obtain that~$T' \eqdef Q \cup \{\alpha'\}$ is the only wiggly pseudotriangulation other than~$T$ containing~$Q$.
\end{proof}

@@

\begin{definition}
\label{def:bijection2}
For a wiggly permutation~$\sigma$ of~$[2n]$, we define~$\Psi(\sigma) \eqdef \set{\alpha(\sigma, k)}{k \in [2n-1]}$, where for~$k \in [2n-1]$, we have~$\alpha(\sigma, k) \eqdef \big( i, j, {]i,j[} \cap \sigma([k]), {]i,j[} \ssm \sigma([k]) \big)$ with
\[
i \eqdef \max \{0\} \cup \set{i \in [n]}{2i-1 \in \sigma([k]) \not\ni 2i} 
\;\text{and}\;
j \eqdef \min \{n+1\} \cup \set{j \in [n]}{2j \in \sigma([k]) \not\ni 2j-1} \!.
\]
\asilata[inline]{I think the correct definition of \(\alpha(\sigma,k)\) is as follows.
  \[\alpha(\sigma,k) = \big(i,j, {]i,j[} \cap \tau(k), {]i,j[} \ssm \tau(k)\big),\]
  where
  \[\tau(k) = \{l \in [n] \mid 2l - 1 \in \sigma([k])\text{ and } 2l \in \sigma([k])\}.\]
}

\end{definition}
